---
title: "23 AUG Meeting"
author: 
date: 
output: 
  ioslides_presentation:
    widescreen: true
    fig_width: 10
    fig_height: 4
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.table.format = "html")
library(tidyverse)
library(ggrepel)
library(sn)
library(e1071)
library(knitr)
library(kableExtra)
```

## Prior Distribution Plots

```{r Prior Distribution Functions, include = FALSE}
estBetaParams <- function(mu.scaled, var.scaled) {
  mu<-mu.scaled/100
  var<-var.scaled/100^2
  alpha <- ((1 - mu) / var - 1 / mu) * mu ^ 2
  beta <- alpha * (1 / mu - 1)
  return(params = list(alpha = alpha, beta = beta))
}
look_at_prior2<-function(muprior,sdprior){
  varprior<-sdprior^2
  pars<-estBetaParams(muprior,varprior)
  alph<-pars$alpha
  bet<-pars$beta
  prior.vals.2<-rbeta(10000,alph,bet)*100
  return(prior.vals.2)
}
```
```{r Prior Distribution Plots}
par(mfrow = c(2, 3))
par(mar = c(5.1, 4.1, 4.1, 2.1))
plot(density(look_at_prior2(70, 5)), main = "Muprior = 70 and SDprior = 5")
plot(density(look_at_prior2(70, 10)), main = "Muprior = 70 and SDprior = 10")
plot(density(look_at_prior2(70, 15)), main = "Muprior = 70 and SDprior = 15")
plot(density(look_at_prior2(70, 20)), main = "Muprior = 70 and SDprior = 20")
plot(density(look_at_prior2(70, 25)), main = "Muprior = 70 and SDprior = 25")
plot(density(look_at_prior2(70, 30)), main = "Muprior = 70 and SDprior = 30")
```

##Bayes vs Boostrap CIs

```{r Bayes vs Boostrap CI Tidy Data, include = FALSE}
combined_results <- read.csv("./Results/bayes_vs_bootstrap_full_data_set.csv")
width_results <- combined_results %>% select("trial", "N.pop", "skew", starts_with("width"))

names(width_results) <- substring(names(width_results), 7)
new_col_names <- c("Trial", "N.pop", "Skew", "T Dist", "BCaExp", "Bayes SDP5", 
                   "Bayes SDP10", "Bayes SDP15", "Bayes SDP20", "Bayes SDP25",
                   "Bayes SDP30")
colnames(width_results) <- new_col_names

width_results <- width_results %>% gather("T Dist", "BCaExp", "Bayes SDP5", 
                                          "Bayes SDP10", "Bayes SDP15", "Bayes SDP20", 
                                          "Bayes SDP25", "Bayes SDP30",
                                          key = "CI.type", value = "width")


#Generate boxplot for different width CIs

means <- aggregate(width ~ CI.type + Skew, width_results, mean) #calculate means by CI.type to generate labels
```
```{r Bayes vs Boostrap CI Plot, fig.width = 10, fig.height = 5}
width_results %>% group_by(CI.type) %>% arrange(desc(CI.type)) %>% 
  ggplot(aes(x = as.factor(CI.type), y = width)) +
  geom_boxplot() +
  geom_hline(yintercept = 6.2) +
  geom_hline(yintercept = 20) +
  stat_summary(fun.y = mean, colour = "darkred", 
               geom="point", shape = 18, size = 3, show.legend = FALSE)+
  geom_text_repel(data = means, aes(label = round(width, digits = 2))) +
  facet_wrap(~Skew, labeller = label_both) +
  coord_flip() +
  #ggtitle("Bayes vs. Bootstrap CIs")
```
<div class="notes">
- N.pop = 10
- N.trials = 100
- Mu Prior = 70
</div>

##Cover Perentages

```{r}
cover_percentages <- combined_results %>% group_by(skew) %>% select("skew", starts_with("cover")) %>% 
  summarise_each(mean)
colnames(cover_percentages) <- c("skew", "Tdist", "BCaExp", "BayesSDP5", "BayesSDP10", "BayesSDP15",
                                  "BayesSD20", "BayesSDP25", "BayesSDP30")

cover_percentages %>% kable() %>% kable_styling(font_size = 20) %>% 
  column_spec(1, bold = T) %>% 
  column_spec(2, width = "15cm")
```

## Full Bayes with Bootstrap CIs {.smaller}

```{r full bayes, include = FALSE}
full_bayes <- read.csv("./Results/full_bayes_with_sdprior_20_v2.csv")
#Making Data Tidy To Plot######
width_results <- full_bayes %>% select("trial", "N.pop", "skew", starts_with("width"))

names(width_results) <- substring(names(width_results), 7)
new_col_names <- c("Trial", "N.pop", "Skew", "T Dist", "BCaExp", "Bayes SDP20")
colnames(width_results) <- new_col_names

width_results <- width_results %>% gather("T Dist", "BCaExp", "Bayes SDP20", 
                                          key = "CI.type", value = "width")


#Generate boxplot for different width CIs

means <- aggregate(width ~ CI.type + Skew, width_results, mean) #calculate means by CI.type to generate labels

```
```{r}
width_results %>% group_by(CI.type) %>% arrange(desc(CI.type)) %>% 
  ggplot(aes(x = as.factor(CI.type), y = width)) +
  geom_boxplot() +
  geom_hline(yintercept = 6.2) +
  geom_hline(yintercept = 20) +
  stat_summary(fun.y = mean, colour = "darkred", geom="point", 
               shape = 18, size = 3, show.legend = FALSE)+
  geom_text_repel(data = means, aes(label = round(width, digits = 2))) +
  facet_wrap(~Skew, labeller = label_both) +
  coord_flip() +
  #ggtitle("Full Bayes vs Tdist vs BCa Bootstrap")
```
<div class="notes">
- N.pop = 10
- N.trials = 100
- Mu Prior = 70
</div>

##Cover Percentages

```{r}
full_bayes %>% group_by(skew) %>% select("skew", starts_with("cover")) %>% 
  summarise_each(mean) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped") %>% 
  column_spec(1, bold = T)
```

##Mixture Distributions {.smaller}

```{r, include = FALSE}
#Distribution 1
sn_mean1 <- 40
sn_stdev1 <- 12.5
sn_skew1 <- 0.5  
cp1 <- c(mean=sn_mean1, s.d.=sn_stdev1, gamma1=sn_skew1)
dp1 <- cp2dp(cp1, family="SN") # the cp2dp function converts the centered parameterization
LB.for.prob1<-psn(0, dp=dp1) # finds the probability associated with the minimum SUS
UB.for.prob1<-psn(100, dp=dp1) # finds the probability associated with the maximum SUS
#Distribution 2
sn_mean2 <- 70
sn_stdev2 <- 12.5
sn_skew2 <- -0.5  
cp2 <- c(mean=sn_mean2, s.d.=sn_stdev2, gamma1=sn_skew2)
dp2 <- cp2dp(cp2, family="SN") # 
LB.for.prob2<-psn(0, dp=dp2) # finds the probability associated with the minimum SUS
UB.for.prob2<-psn(100, dp=dp2) # finds the probability associated with the maximum SUS

n <- 1000
w <- rbinom(n, 1, 0.5) #samples to create a probability for each cluster
data = vector(length = n)
a = 1
#Loop to generate data from a mixture distribution
for(i in w){
  if (i == 1) {
    data[a] = qsn(runif(n=1,min=LB.for.prob1,max=UB.for.prob1), dp=dp1, solver="RFB")
    a <- a +1
  }
  else{
    data[a] = qsn(runif(n=1,min=LB.for.prob2,max=UB.for.prob2), dp=dp2, solver="RFB")
    a <- a + 1
  }
}
  
```
```{r Mixture Distribution Plot}
mix <- density(data)
hump1 <- density(qsn(runif(n=500,min=LB.for.prob1,max=UB.for.prob1), dp=dp1, solver="RFB"))
hump2 <- density(qsn(runif(n=500,min=LB.for.prob2,max=UB.for.prob2), dp=dp2, solver="RFB"))

plot(range(mix$x, hump1$x, hump2$x), range(mix$y, hump1$y, hump2$y), type = "n", 
     xlab = "x", ylab = "Density")
lines(hump1, col = "red") 
lines(hump2, col = "blue")
lines(mix)

```
$f(y_{i}) = f_{1}(y_{i} \mid \theta_{1} = 40)^{z_{i}}f_{2}(y_{i} \mid \theta_{2} = 70)^{1-z_{i}}$

$y_{1} \sim SN(\mu_{i},  \sigma = 12.5, \gamma = 0.5)$, 
$y_{2} \sim SN(\mu_{2}, \sigma = 12.5, \gamma = -0.5)$, 
$z_{i} \sim Ber(p)$

## Mixture Distributions with Different Mean Combinations

<style>
.column-left{
  float: left;
  width: 35%;
}

.column-right{
  float: right;
  width: 40%;
}
</style>

```{r import_csvs, include = FALSE}
mixture.25 <- read.csv("./Results/mixture_bootstrap_n.pop25_trial100_v2.csv")
mixture.10 <- read.csv("./Results/mixture_bootstrap_n.pop10_trial100_v2.csv")
```
<div class = "column-right">
```{r}
mixture.25 %>% group_by(mean1, mean2) %>% 
  summarize(
    avgcorrect = mean(perc.correct)
  ) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>% 
  footnote(general = "N.pop = 25, N.trials = 100")
```
</div>

<div class = "column-left">
```{r}
mixture.10  %>% group_by(mean1, mean2) %>% 
  summarize(
    avgcorrect = mean(perc.correct)
  ) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>% 
  footnote(general = "N.pop = 10, N.trials = 100")
```
</div>


## Mixture Distribution with Different Prior Mu Combinations

```{r}
combined_muprior <- read.csv("./Results/mixture_bootstrap_mean70_changing_muprior.csv")

combined_muprior %>% group_by(mean1, mean2, muprior1, muprior2) %>% 
  summarise(
    avg_correct = mean(perc.correct)
  ) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped", full_width = F) %>% 
  footnote(general = "N.pop = 25, N.trials = 100")
```



